OSF management

### 2021-12-15 osf/manage-osf.Rmd
🐛 - fix missing trial-lists

for (tlist in tlists) {
  speaker <- str_sub(tlist, 20, 21)
  tbl <- read_csv(tlist) %>%
    mutate(
      speaker = speaker,
      trial = row_number()
    ) %>%
    left_join(y = typ) %>%
    select(speaker, trial, condition, typicality, everything()) %>%
    mutate(typicality = ifelse(condition == "NF", typicality, NA)) %>%
    left_join(y = ratings_summary, by = c("target_name" = "object", "target_colour" = "colour"))

>>>>

for (tlist in tlists) {
  speaker <- str_sub(tlist, 20, 23) %>%
    str_remove("\\.c")
  tbl <- read_csv(tlist) %>%
    mutate(
      speaker = speaker,
      trial = row_number()
    ) %>%
    left_join(y = typ) %>%
    select(speaker, trial, condition, typicality, everything()) %>%
    mutate(typicality = ifelse(condition == "NF", typicality, NA)) %>%
    left_join(y = ratings_summary, by = c("target_name" = "object", "target_colour" = "colour"))
